\documentclass[100pt]{article}
\usepackage[italian,american]{babel}
\usepackage[utf8]{inputenc}
\usepackage{fancyhdr}
\usepackage{amsmath,amssymb,amsthm}
\usepackage{minted}
\usepackage[a4paper, left=0.911in, right=0.911in]{geometry}
\usepackage{hyperref}
\usepackage{calc}
\usepackage{listings}
\usepackage{wrapfig}
\usepackage{graphicx}
\usepackage{xcolor}
\definecolor{keywords}{RGB}{255,0,90}
\definecolor{comments}{RGB}{0,0,113}
\definecolor{red}{RGB}{160,0,0}
\definecolor{green}{RGB}{0,150,0}
\definecolor{bluino}{RGB}{4, 55, 242}
\definecolor{carota}{rgb}{0.93, 0.57, 0.13}
\definecolor{black}{rgb}{0.0, 0.0, 0.0}
\definecolor{rosino}{rgb}{0.87, 0.36, 0.51}
\definecolor{cadetblue}{rgb}{0.1, 0.1, 0.70}
\pagenumbering{arabic}
\pagestyle{plain}
\usepackage{setspace}
\usepackage{enumitem}

\begin{document}


\setlength{\headsep}{35pt}
\fancyhf{}
\fancyhead[R]{\color{bluino} \small Daniele Bugatti, Nicole Dupertuis, \\ Amanda Giacomuzzi, Namdoel Oberholzer}
\fancyhead[L]{\color{bluino} \small D-HEST \\ Foundations of Data Science}

\renewcommand\headrulewidth{0pt}
\pagestyle{fancy}

\begin{huge}
\begin{center}
Escherichia coli Ceftriaxone resistance
\break
\end{center}
\end{huge}


\begin{normalsize}\color {bluino}
\noindent Overview of the Dataset:\\
---------------------------------------------------------------------------------------------------------------------------------------------
\end{normalsize}

\begin{normalsize}

COULD SOME OF YOU DO A LITTLE RESEARCH ON THE DATASET?

this should start like:\\

Antibiotic resistance is one of the most important topics in modern medicine, the dataset....\\

Topic: Antibiotic resistance - Escherichia coli Ceftriaxone resistance

Summary: Antibiotic resistance is one of the most interesting topics of medical research and poses a growing challenge in current treatment and prevention of infections. The DRIAMS data set comprises information on mass spectroscopy analysis of bacteria extracted from patients treated at four different medical institutions. These spectra can give information regarding different phenotypes of the bacteria which in turn may inform on their specific antibiotic resistances. We selected three pairs of bacterial species and antibiotic treatments as examples from this large data set. The aim of an analysis would be to analyse the presence of different bacteria subgroups within a data set and/or associations with treatment response.
Data details: 1368 samples, 6000 MALDITOF features

References:

\url{https://datadryad.org/stash/dataset/doi%253A10.5061%252Fdryad.bzkh1899q}
\url{Weis, C., Cuénod, A., Rieck, B. et al. Direct anMmicrobial resistance predicMon from clinical MALDI-TOF mass spectra using machine learning. Nat Med 28, 164–174 (2022).https://doi.org/10.1038/s41591-021-01619-9}


\end{normalsize}

\begin{normalsize}\color {bluino}
\hfill\break

\noindent Data Preprocessing and Visualization:\\
---------------------------------------------------------------------------------------------------------------------------------------------
\end{normalsize}

\begin{normalsize}

The dataset was 

\end{normalsize}








%%				cd  /Users/user/Desktop/project/project/report 			pdflatex -shell-escape Report.tex


\end{document}

